Thread Pool in GeckoDB/BOLSTER - Integrating a Thread Pool into a high performance Database System \\

### 2018-06-11 Presentations/Milestone3/presentation.tex
Fix Milestone 3 and paper

@@

\begin{frame}
	\frametitle{Evaluation Setup}
	\begin{itemize}
		\item Use of geckodb to stress test the thread pool by with BOLSTER primitives
		\item Measure different statistics for tasks, thread and thread pools
		\item Use statistics to determine optimal configurations for different thread pool instances
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Thread Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			waiting\_time & Time the thread spend waiting (ms) \\
			busy\_time & Time the thread spend executing tasks (ms)\\
			task\_count & Number of tasks the thread has executed \\
			\hline
		\end{tabular}
		\label{tab3}
	\end{center}
	\begin{itemize}
		\item $waiting\_time$ of threads indicate a good thread pool size
		\item $task\_count$ interesting to number of all completed tasks
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Thread Pool Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			working\_time & Time the thread pool runs (ms) \\
			task\_complete\_count & Number of completed tasks \\
			task\_enqueued\_count & Number of enqueued tasks \\
			avg\_complete\_time & Average time span from enqueueing until \\
			& execution of tasks \\
			avg\_wait\_time & Average time of tasks spend in the queue \\
			\hline
		\end{tabular}
		\label{tab4}
	\end{center}
	\begin{itemize}
		\item $avg\_wait\_time$ indicates the quality of the chosen thread pool size
	\end{itemize}
\end{frame}

>>>>

\begin{frame}
	\frametitle{Usage Examples}
	\begin{center}
		\includegraphics[width=0.95\textwidth]{img/thread_pool_use.png}
	\end{center}
\end{frame}

\begin{frame}
\frametitle{Usage Examples}
\begin{center}
	\includegraphics[width=0.95\textwidth]{img/thread_pool_use2.png}
\end{center}
\end{frame}

@@

\begin{frame}
	\frametitle{Evaluation Setup}
	\begin{itemize}
		\item Use of geckodb to stress test the thread pool by with BOLSTER primitives
		\item Measure different statistics for tasks, thread and thread pools
		\item Use statistics to determine optimal configurations for different thread pool instances
		\item Time measures are taken with wall clock time
	\end{itemize}
\end{frame}

@@

\begin{frame}
	\frametitle{Thread Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			waiting\_time & Time the thread spend waiting (ns) \\
			busy\_time & Time the thread spend executing tasks (ns)\\
			task\_count & Number of tasks the thread has executed \\
			\hline
		\end{tabular}
		\label{tab3}
	\end{center}
	\begin{itemize}
		\item $waiting\_time$ of threads indicate a good thread pool size
		\item $task\_count$ interesting to number of all completed tasks
	\end{itemize}
\end{frame}

\begin{frame}
	\frametitle{Thread Pool Statistics}
	\begin{center}
		\begin{tabular}{ c c }
			\hline
			\textbf{Statistic name}&\textbf{Description}\\
			\hline
			working\_time & Time the thread pool runs (ns) \\
			task\_complete\_count & Number of completed tasks \\
			task\_enqueued\_count & Number of enqueued tasks \\
			avg\_complete\_time & Average time span from enqueueing until \\
			& execution of tasks \\
			avg\_wait\_time & Average time of tasks spend in the queue \\
			\hline
		\end{tabular}
		\label{tab4}
	\end{center}
	\begin{itemize}
		\item $avg\_wait\_time$ indicates the quality of the chosen thread pool size
	\end{itemize}
\end{frame}

### 2018-06-11 Presentations/Paper/paper_thread_pool.tex
Add Milestone 3 presentation (not complete)
Fix Milestone 3 and paper

In the next step, the tasks will be enqueued into the priority queue of the thread pool. Optionally, a handle can be passed with the tasks or generated by the thread pool to force the calling function to wait for the tasks. After enqueueing the tasks to the priority queue, the waiting threads in the thread pool pop the enqueued tasks from the priority queue and executes the routine of the task. This happens asynchronously to the calling function and therefore is not considered as an own step of the process.

The third step is only executed if the tasks refer to a valid handle and waiting is enforced by the calling function. This can be applied either by executing a provided waiting function from the thread pool or by calling \emph{thread\_pool\_enqueue\_tasks\_wait}. We will present our design of waiting for a specific amount of tasks in Section 3.D. The last step only contains the return to the calling function.

>>>>

In the next step, the tasks will be enqueued into the priority queue of the thread pool. Before enqueueing, the function \emph{thread\_pool\_enqueue\_tasks\_wait} creates a handle and links all tasks to it. After enqueueing the tasks to the priority queue, the waiting threads in the thread pool pop the enqueued tasks from the priority queue and execute the routine of the task. This happens asynchronously to the calling function and therefore is not considered as an own step of the process. The calling threads gets one of the passed tasks and processes it. After finishing the task, the calling thread waits until all other tasks referring to the created handle are finished and then returns to the calling function. In the next section, we show the waiting for tasks with handles in detail.
